---
title: "COVID-19"
output: 
  html_document: 
    keep_md: yes
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(janitor)
library(here)
library(naniar)
library(skimr)
```



```{r}
covid <- read.csv("Data/WHO-COVID-19-global-data.csv")
```

```{r}
covid<-janitor::clean_names(covid)
```

```{r}
covid$nuo_daiate_reported <- lubridate::mdy(covid$nuo_daiate_reported)
```


```{r}
covid$nuo_daiate_reported <- as.Date(covid$nuo_daiate_reported)
covid$cumulative_cases <- as.numeric(as.character(covid$cumulative_cases))
```


```{r}
head(covid)
```
```{r}
glimpse(covid)
```
```{r}
skim(covid)
```
#### NAs are represented by "NA" or "########"



```{r}
covid %>% 
  group_by(country) %>% 
  arrange(desc(cumulative_cases))
```
```{r}
covid %>% 
  filter(nuo_daiate_reported== "2021-02-11") %>% 
  arrange(desc(cumulative_cases))
```
#### We're going vaccine data for the top 5 countries with the most COVID-19 cases to date.  USA, India, Brazil, Russian Federation, UK.

```{r}
covid %>%
  filter(nuo_daiate_reported=="2021-02-11")%>%
  ggplot(aes(x=cumulative_cases))+
           scale_y_log10()+
           geom_density()
```

##### We have to figure out how to make this not a logarithmic scale.

##### We can use faceting to compare cases.

##### Use pivot wide to analyze a single country over time.
```{r}
covid$date_reported <- as.Date(covid$date_reported)
covid$cumulative_cases <- as.numeric(as.character(covid$cumulative_cases))
```

```{r}
covid%>%
  filter(country_code == "US")%>%
  ggplot(aes(x = nuo_daiate_reported, y = cumulative_cases))+
  geom_line(aes(group = 1))+
  scale_x_date(date_labels = "%Y-%m-%d")+
  scale_x_date(date_breaks = "1 month")+
  scale_y_continuous(breaks = seq(0, 30000000, by = 2500000), limits=c(0, 30000000))+
  theme(axis.text.x=element_text(angle=45, hjust=1)) 
```

##### Create comparative plots
```{r}
covid%>%
  group_by(country)%>%
  filter(country_code == "US"| country_code == "IN"| country_code == "BR"| country_code == "RU"| country_code == "GB")%>%
  ggplot(aes(x = nuo_daiate_reported, y = cumulative_cases, group = country, color = country))+
  geom_line()+
  scale_x_date(date_labels = "%Y-%m-%d")+
  scale_x_date(date_breaks = "1 month")+
  scale_y_continuous(breaks = seq(0, 30000000, by = 2500000), limits=c(0, 30000000))+
  theme(axis.text.x=element_text(angle=45, hjust=1)) 
```

##### Find data on populations + governments of these countries to compare the covid data. (Along with vaccine data)
```{r}

```

##### Maybe make a website that showcases our analysis of this data.
